Modeling tactical and memory-driven migration in dynamic environments

### 2021-03-25 presentations/memorymigration_v2.Rmd
updates

---
title: "Modeling tactical and memory-driven migration in dynamic environments"
author: "Sriya Potluri and Elie Gurarie"
date: "3/24/2021"
output: slidy_presentation
---

@@

<div class='left' style='float:left;width:60%'>
actic response**
2. High overall mobility (high tactic + high diffusion) =  high foraging efficiency
3. Slow diffusion leads to longer time to attain equilibrium

@@

1. This is a convenient, flexible and fast tool for exploring a wide range of memory / tactic / sociality dynamics

>>>>

---
title: "Modeling tactical and memory-driven migration in dynamic environments"
author: "Elie Gurarie, Sriya Potluri, Bill Fagan"
date: "3/24/2021"
output: slidy_presentation
---

@@

<div class='left' style='float:left;width:60%'>
1. Highest mirgation with **low diffusion** but **high tactic response**
2. High overall mobility (high tactic + high diffusion) =  high foraging efficiency
3. Slow diffusion leads to longer time to attain equilibrium

@@

1. This is a convenient, flexible and fast tool for exploring a wide range of memory / tactic / sociality dynamics
2. Plusses / Minusses versus individual-based approach?
